---
title: "P8105 HW 1"
author: Yuki Low (yl5503)
date: 09/15/2023
output: github_document
---

**Problem 1**

Loading data and the libraries needed for this homework:

```{r message = FALSE}
library(moderndive)
library(ggplot2)
library(tidyverse)
data("early_january_weather")
```

```{r}
temps <- pull(early_january_weather, temp)
```

There are `r ncol(early_january_weather)` variables in this dataset named `early_january_weather`. The only character variable in this dataset is `origin`. The integer variables are as follows: `year`, `month`, `day`, `hour`. The numerical variables are as follows: `temp`, `dewp`, `humid`, `wind_dir`, `wind_speed`, `wind_gust`, `precip`, `pressure`, `visib`. The only POSIXct variable is `time_hour`. The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature is `r mean(temps)` degrees.

```{r}
scatterplot <- ggplot(early_january_weather, mapping = aes(x = time_hour, y = temp, color = humid)) +    geom_point() + 
  labs(x = "Time Hour", y = "Temperature", title = "Scatterplot of Temperature vs. Time Hour")

ggsave("scatterplot.png", plot = scatterplot, width = 8, height = 6)

scatterplot

```

The scatterplot of `temperature` vs. `time_hour` exhibits a repeating, cyclic pattern suggesting a daily weather pattern which can indicate that temperature and time hour follow a predictable trend over the course of the day. The scatterplot also shows a clear gradient from dark blue to light blue which can indicate that humidity increases as time hour increases in the month of January. The scatterplot also has an overall increasing trend which can indicate that temperature increases as time hour increases in the month of January.

**Problem 2**

```{r warning=FALSE}
problem_2_df <- tibble(
  samples = rnorm(10),
  log_vector = c(samples > 0),
  char_vector = c('a','b','c','d','e','f','g','h','i','j'),
  factor_vector = as.factor(c('small', 'medium', 'small', 'medium', 'large', 'large','medium','large','medium','large'))
  
)

samples_mean <- mean(pull(problem_2_df,samples))
log_mean <- mean(pull(problem_2_df,log_vector))
char_mean <- mean(pull(problem_2_df,char_vector))
factor_mean <- mean(pull(problem_2_df,factor_vector))
```

- The mean of the: 
  - samples vector is `r samples_mean`.
  - log_vector is `r log_mean`. 
  - char_vector is `r char_mean`. 
  - factor_vector is `r factor_mean`.

You are only able to find the means of the random sample vector and the logical vector.

```{r warning = FALSE}
new_log_mean <- mean(as.numeric(pull(problem_2_df,log_vector)))
new_char_mean <- mean(as.numeric(pull(problem_2_df,char_vector)))
new_factor_mean <- mean(as.numeric(pull(problem_2_df,factor_vector)))
```

- The mean of the: 
  - new log_vector is `r new_log_mean`.
  - new char_vector is `r new_char_mean`.
  - new factor_vector is `r new_factor_mean`.
  
The log_vector and factor_vector were converted into numerical vectors. For the logical vector, `TRUE` and `FALSE` values turned into `0` and `1` whereas for the factor vector, `small`, `medium`, `large` values turned into `0`, `1`, `2`. Since the `factor_vector` is now converted into a numeric vector, we can now find the mean. However, when the as.numeric function is being applied to the char vector, it does not know what numeric value to convert each of the chars to. Therefore, each char does not have a numeric representation and therefore, we are unable to find the mean even after applying the as.numeric function.


